Spirals launched by a planet in a shadowed disk

### 2024-04-14 src/tex/ms.tex
Start results section

$\Delta \rho_{\rm shadow}$ is determined from our shadow-only simulations (\texttt{narrow\_without} and \texttt{wide\_without}).

@@

>>>>

$\Delta \rho_{\rm shadow}$ is determined from our shadow-only simulations (\texttt{narrow\_without} and \texttt{wide\_without}). See Figures \ref{fig:sp_narrow}
\& \ref{fig:sp_wide} for this residual in the narrow and wide cases, respectively.

@@

\begin{figure}
    \begin{center}
        \includegraphics[width=0.5\textwidth]{figures/zeta_narrow.pdf}
        \script{plot_zeta_narrow.py}
        \caption{
            The pitch angle $\zeta$ for the narrow case. Far from the planet there is some discontinuous variability introduced by the shadow.
            The planet-only case fits well to the analytic approximation.
        }
        \label{fig:zeta_narrow}
    \end{center}
\end{figure}

\begin{figure}
    \begin{center}
        \includegraphics[width=0.5\textwidth]{figures/zeta_wide.pdf}
        \script{plot_zeta_wide.py}
        \caption{
            Same as Figure \ref{fig:zeta_narrow} but for the wide case. Note that the variations in the inset are much more continuous than in the
            narrow case, and have a much larger amplitude.
        }
        \label{fig:zeta_wide}
    \end{center}
\end{figure}

The shape of a spiral can be parameterized by its initial condition $\phi(r_0)$ and by its pitch angle $\zeta$. Pitch angle
is defined as
\begin{equation}
    \cot \zeta = \frac{d\phi}{d \ln r}
\end{equation}

according to \citet{zhu2022}. We use a central difference scheme to take the numerical derivative of $\phi_{\rm peak}$ with respect to $\ln r$.
